Superabsorption of light by nanoparticles

### 2015-10-08 2015-Ladutenko-Qabs/submission-nanoscale/comm_template/response-letter/response-letter.tex

\newpage
\textbf{Reviewer \#1 comments}

\begin{tabular}[!H]{l|p{0.9\textwidth}}
\quad & 1. The authors claimed “Combined effect of these resonances is
presented to produce the flat and relative broadband electric
resonance response.” Nevertheless, the broadened absorption band is
not very broad. Is there any further way to predict a broadband light
absorption. For instance, a broadband absorption in the whole visible
spectral range. Maybe, a possible way of using the dispersed size
scale nanoparticles should be added for improving the study.
\end{tabular}\\

We thank the referee for suggestion. First, we would like to note that
the term "broadband" is quite loose, when not defined explicitly. For
example, if we compare our absorption band with the whole C-band of
the optical fibres, which is used to carry Terabits of data, and which
is just 35 nm wide, then our absorbers are extremely broadband, since
they have the bandwidth approaching 100 nm. Compared to the whole
visible spectrum, however, indeed our absorption band is not very
broad. So, to address the referee comment, we decided to study the
possible ways to enhance the width of the absorption band.

We can think of a two possible approaches to achieve the broadband
performance. First approach utilizes the mix of different particles,
while the second approach uses several resonances within one
particle. The later approach is nontrivial and requires large
additional study, that would deserve a separate publication. The first
approach, however, mentioned by the Referee, is more straightforward,
and we can use a mixture of different particles, so that particles of various sizes absorb different wavelengths.  To illustrate this we have
run an optimization procedure to find two designs: one absorbs at
475~nm, while another is centered at 525~nm (outer radii 34 and 38~nm,
respectively). We then combine such particles to form a dimer, and
calculate its properties using Lumerical FDTD Solutions. Sketch of the
simulated system and final results are shown in
Fig.~\ref{fig:fdtd}. As a reference, we also perform FDTD simulations
of standalone spheres, and the obtained positions and we found that the amplitudes of
resonances match well the results of the Mie calculations.
\begin{figure}
  \begin{minipage}[h]{0.49\textwidth}    \begin{flushleft}     a)    \end{flushleft}
  \end{minipage}
  \begin{minipage}[h]{0.49\textwidth}    \begin{flushleft}     b)    \end{flushleft}
  \end{minipage}
  \begin{minipage}[h]{0.49\textwidth} 
   \includegraphics[width=0.95\textwidth]{FDTD-mode-d00}
  \end{minipage}
  \begin{minipage}[h]{0.49\textwidth} 
   \includegraphics[width=0.95\textwidth]{fdtd-spectra}
  \end{minipage}
  \begin{minipage}[h]{0.49\textwidth}    \begin{flushleft}     c)    \end{flushleft}
  \end{minipage}
  \begin{minipage}[h]{0.49\textwidth}    \begin{flushleft}     d)   \end{flushleft}
  \end{minipage}
  \begin{minipage}[h]{0.49\textwidth} 
    \includegraphics[width=0.95\textwidth]{fdtd-spectra-Ek}
  \end{minipage}
  \begin{minipage}[h]{0.49\textwidth} 
    \includegraphics[width=0.95\textwidth]{fdtd-field}
  \end{minipage}
    \caption{(a) Sketch of the simulated dimer in full wave
      simulations by Lumerical FDTD. (b) Absorption spectra of
      stand-alone spheres and in dimer configuration with separation
      between spheres of 0, 10, and 30~nm, particles are in H-k plane;
      (c) Separation 0 and 30~nm for particles in E-k plane; (d) Field
      distribution for the incident wavelength of 500 nm for particles
      in E-k plane with separation of 30~nm.\label{fig:fdtd}}%
\end{figure}

When we mix the different sized spheres, there will be an effect of
their mutual interaction. To take this into account, we simulate a
dimer configurations with 0 nm, 10 nm and 30 nm separation between
spheres.  The resulting spectra have a strong contribution from
standalone resonances, while coupling effects seems to be relatively
minor. This can be explained from modal field distribution in
Fig.~4(c) of the manuscript. Positioning spheres in H-k plane we are
exploiting the fact that the fields are highly localized inside the
spheres. Arranging spheres in other planes with respect to incident
polarization, or increasing the number of interacting spheres can
change the effect of coupling. As an example, we tested arrangement of
spheres in E-k plane Fig.~\ref{fig:fdtd}(c); for zero separation the
interaction between spheres is strong, however, due to near-field
nature of this coupling, it rapidly decays with the separation width
Fig.~\ref{fig:fdtd}(d), for separation of 30~nm responses of
individual particles dominate in overall spectra for both planes of
polarization. This way we show that in principle it is possible to
construct an absorption band of an array of dispersed particles simply
optimizing the properties of individual particles.

@@

    \caption{ FDTD simulation of a 3x3 array of spheres, which are
      individually optimized for absorption at 525~nm(a) Fullwave
      simulation performed in Lumerical FDTD. (b) Cross-section
      absorption spectra (c,d,e) Field distribution for the
      wavelengths of 408, 452, and 600 nm.\label{fig:fdtd-3x3}}%
\end{figure}

\vspace{10pt}

\newpage
\begin{minipage}{1.0\linewidth}
  \textbf{Reviewer \#2 comments}\\
  \begin{tabular}[!H]{l|p{0.9\textwidth}}
    \quad & 1.  As we can find from the manuscript, the highest
    absorption efficiency is achieved for a Si/Ag core-shell
    structure, which is not located in the super absorbing
    regime. Moreover, the authors also claimed that from practical
    aspect, the core-shell structure (not in the super absorbing
    regime) could be easier and cheaper to fabricate than three
    layered structure (in the super absorbing regime). Therefore, the
    authors should clearly clarify what are the advantages or
    significances of the super absorption nanoparticles?
\end{tabular}
\end{minipage}

The super-absorption has a physical meaning of a regime, when we
create a structure, which has several highly absorbing resonances
overlapping in frequency, so that total absorption is larger than what
can be created in the structure with just one resonance. The main conclusions of the paper are
that a) We can create structures that shows superabsorption b) For
small particles (below 60nm), the efficiency of absorption is higher
in a single mode regime.  c) For larger particles the superabsorption
regime allows to achieve best efficiency of absorption.

@@

To make this more clear in the manuscript, we have made the following changes to the manuscript:

In the end of the first paragraph of page 3, right column, after
``..., since it should be easier and cheaper to fabricate.'' We add:
``At the same time the best absorption efficiency for larger particles
(with $R>60$~nm for provided materials) can be achieved in
superabsorption regime. This may be important when fabrication of
smaller multi-layer particles is not available.''

\begin{tabular}[!H]{l|p{0.9\textwidth}}
  \quad & 2.  In Fig. 2, we noticed a discontinuity at $\sim$80
  nm. The authors explain it as the design supporting electric dipole
  and magnetic quadrupole has larger ACS. However, this explanation is
  not clearly to me since it is lacking physics behind this
  phenomenon. The authors should clarify why the magnetic quadrupole
  only plays a significant role in this small wavelength range.
\end{tabular}

The short qualitative answer to this is that it is not possible to
excite the magnetic quadrupole resonance to the particle of a smaller
size, and, it is hard to make it absorb efficiently for larger sizes, while
also maintaining the large contribution of the electric dipole.

To present this idea in more details we run an optimization with
changed fitness function - we maximize the absorption efficiency of
only the electric dipole, with results presented in
Fig.~\ref{fig:a1max}. With the increase of the particle radius $R$, the electric dipole contribution
$\tilde{a}_1$ rapidly reaches its theoretical maximum. Optimizer was
quite successful in maintaining this for all larger values of $R$. When
we increase the $R$, other multipole resonances can appear. Such an
appearance of magnetic quadrupole term $\tilde{b}_2$ forms the discussed maxima at $\sim
80$~nm, and it is clearly observed in Fig.~\ref{fig:a1max}(b).

@@

Another way to qualitatively explain the effect is the following. We
have a multiple resonance structure, and by changing parameters we can
overlap several different resonances. Depending on the total particle
size, different combination of resonances can give maximum absorption,
therefore it is not surprising that in a certain parameter range, the
combination of electric dipole and magnetic quadrupole can give us the
best possible absorption.

\begin{figure}
  \includegraphics[width=0.35\textwidth]{overview-Qabs-a1}
   \includegraphics[width=0.60\textwidth]{overview-Qabs-all-a1}
  \caption{(a-c) Same as Fig.2 of the manuscript with different
    fitness function: the optimization aims to maximize the electric
    dipole absorption. (Missing points did not pass the stability
    test.) (d) $Q_{abs}$ for maximized $\tilde{a}_1$ from the first
    subplot of present figure without the additional stability test
    (green line) compared with $Q_{abs}$ optimization regarding all
    multipoles (black line, same as in Fig 2(a) of the
    manuscript).\label{fig:a1max}}
\end{figure}

\begin{tabular}[!H]{l|p{0.9\textwidth}}
\quad & 3.  In Fig. 3 (c), the authors observed a flat top of electric
dipole resonance. They attributed this flat resonance to the excited
several electric dipole resonances with close resonance
frequencies. Nevertheless, as we can see in Fig. 3 (d), even without
considering the resonances located in outer and inner shell, the
resonance inside the core is much broader than the other two
cases. The authors should explain this broadened resonance clearly.
\end{tabular}

We thank the referee for pointing this out, we must have not explained
this point clearly. The most interesting feature of this resonance
that we wanted to bring attention to is that the resonance has an
unusual flat top. The main shape and width of the resonance is
explained by one dominating dipole mode, as it is seen in the mode
decomposition in Fig.~3(d). Two additional electric dipole resonances
are much weaker, but their contribution "flattens" the top of the
combined absorption resonance. We have clarified this in the modified
manuscript changing the caption of Fig.~(3), after ``Panel~(d) shows
the superposition of the squared absolute values of the Mie
coefficients for electric dipole contribution inside each layer'' we
added ``of design from panel~(c), and it explains an almost
flat top of the electric dipole resonance.''

@@

\begin{tabular}[!H]{l|p{0.9\textwidth}}
\quad & 4.  Some sentences are not clear to me. For instance, “there
is a strong conterplay between the increased absorption for larger
particles vs size for smaller particles”.  In summary, I do not think
the manuscript is acceptable at its current stage.
\end{tabular}%

We have worked on improving the readability of the
manuscript. Particularly, we changed the instance mentioned with the
reviewer, full sentence in the updated manuscript is now the
following: ``The absorption efficiency can be made large either by increasing ACS while keeping the particle size fixed, or by decreasing the particle size for fixed ACS. As a result, we show in this paper that smaller particles are more efficient when they operate in a single mode regime, while larger particles are more efficient absorbers when multiple modes are excited at the same frequency. ''
\end{document}

### 2015-10-08 2015-Ladutenko-Qabs/submission-nanoscale/comm_template/2015-Ladutenko-Qabs.tex

\sffamily{\textbf{  Nanoparticles have a fundamental limit as to how much light they can
  absorb. This limit is based on the finite number of modes excited in
  the nanoparticle at a given wavelength and maximum absorption
  capacity per mode. The enhanced absorption can be achieved when each
  mode supported by the nanopartice absorbs light up to the maximum
  capacity. Using stochastic optimization algorithm, we design
  multilayer nanoparticles, in which we can make several resonant
  modes overlap at the same frequency resulting in \textit{
    superabsorption}.  We further introduce the \textit{ efficiency of the
    absorption} for a nanoparticle, which is the absorption normalized
  by the physical size of the particle, and show that efficient
  absorbers are not always operating in the superabsorbing regime.}}\\%The abstrast goes here instead of the text "The abstract should be..."

@@

Mie theory,\cite{Mie-1908} which is over 100 years old, describes
interaction of electromagnetic waves with spherical particles. Mie
solution is still of great interest these
days,\cite{Suzuki-2008,MacKowski-2012,Lerme-2000,Xu-2005,Li-2006,Gogoi-2010,Santiago-2011}
since it is one of the primary tools for analyzing wave scattering by
spherical objects. Further development of the Mie
theory\cite{Yang-2003, Pena-scattnlay-2009} made it possible to apply
it to the study of multilayer spherical
particles.\cite{Sheehan-2013,Selmke-2012}  Such particles have
various applications in cancer treatment,\cite{Zhang-2010,
  Hirsch-2003} medical diagnostics,\cite{Allain-2002}
cloaking\cite{Qui-2009, Semouchkina-2013, Ladutenko-2014} and
plasmonic devices,\cite{Liu-MatLett-2015, Martin-2013, Alu-2005, Liu-Nanotech-2013} in the study of
thermal properties of insulating materials,\cite{Xie-2013} as well as
for improving solar cells performance.\cite{Kameya-2011,Mann-2011}

@@

Similar fundamental limitations exist for the absorbing properties of
subwavelength nanoparticles.  Tribelsky\cite{Tribelsky-2011} has
derived a theoretical limit of a maximum absorption cross-section
(ACS) value for a single channel, i.e., when only one mode of a sphere
is excited.  As a result, the absorption coefficients $\tilde{a}_n=
{\rm Re}\{a_n\} - |a_n|^2 $ and $\tilde{b}_n= {\rm Re}\{b_n\} -
|b_n|^2 $ become limited by $1/4$, here $a_n$ and $b_n$ are scattering
coefficient as defined within the Mie theory\cite{Bohren-1983} for
expansion of the scattered electric field:
\[
{\rm \mathbf{E}}_s = \sum_{n=1}^{\infty} E_n \left( i a_n {\rm
    \mathbf{N}}_{e1n}^{(3)} - b_n{\rm\mathbf{M}_{o1n}^{(3)}} \right),
\]
where ${\rm \mathbf{N}}_{e1n}^{(3)}$ and ${\rm\mathbf{M}_{o1n}^{(3)}}$
are corresponding vector spherical harmonics,
$E_n=i^nE_0(2n+1)/n(n+1)$, $n$ is the angular momentum of the mode,
and $E_0$ is the amplitude of the incident field.

To overcome these limitations, we employ similar approach to the one
used for enhancing scattering cross-section.\cite{Fan-2011} In
particular, we propose to use the multilayer structures, and by means
of stochastic optimization algorithm\cite{Jingqiao-JADE-2009} we
optimize the ACS of such nanoparticles. We analyze the absorption
cross-section of these particles, and present the superabsorption
regime. We further introduce the absorption efficiency, which is the
ACS normalized to the geometric cross-section of particles.  Here we
show that the increased peak absorption rate of high order multipoles
available in larger particles does not compensate the increased volume
with low absorption rate compared to volume of smaller particles, and
quite remarkably we find that the most {\em efficient} absorption can
be achieved in a single channel limit for small particles.

Another approach for an ideal absorber is given in the recent work by
Grigoriev et al.\cite{Grigoriev-2015} Authors considered only dipole
approximation, and the final result is very close to the dipole limit
predicted by Tribelsky.\cite{Tribelsky-2011}  Such absorption design
corresponds to the single mode limit.  At the same time, Grigoriev et
al.\cite{Grigoriev-2015} also provide an equation to design a
core-shell structure from given materials. However, in the case of
$Si$ core and $Ag$ shell materials and sizes taken from the best
design obtained in the present paper, their equation gives a complex
value for the core material filling factor, which cannot be achieved
in experimental realisations.

@@

The proposed approach can be applied to arbitrary combination of
materials, but to be more specific in what follows we consider
dielectric-metal-dielectric triple-layer $Si/Ag/Si$ spherical particle
illuminated by a plane wave schematically shown in
Fig.~\ref{fig:geom}. In what follows we describe the materials using
experimentally measured parameters from Ref.,\cite{palik-1997}
e.g. at $\lambda = 500$ nm $\epsilon_{Si} = 18.5 + i0.63$ and
$\epsilon_{Ag} = -8.5 + i0.76$.  To optimize the thickness of each
layer we implemented\cite{JADE-web} an adaptive differential
evolution algorithm,\cite{Storn-DE-first-1997} which is called
JADE.\cite{Jingqiao-JADE-2009}  The technical details of the
optimization algorithm were published previously in
Ref.\cite{Ladutenko-2014} We perform Mie calculations using the
Scattnlay software,\cite{Pena-scattnlay-2009,Scattnlay-web} whose
results are verified by a number of other implementations of the Mie
solutions and by commercially available software including CST
Microwave studio\cite{CST-web} and Comsol
Multiphysics.\cite{Comsol-web}

@@

\begin{figure}[h]
  \center{
    % Use pdfcrop to remove white margins
    \includegraphics[width=0.45\textwidth]{2015-04-01-SiAgSi-ab-spectra4}%
    \caption{Spectra of Mie absorption coefficients of (a)~efficient
      and (b-c)~superabsorption design. Panel~(d) shows the
      superposition of the squared absolute values of the Mie
      coefficients for electric dipole contribution inside each layer
      of design from panel~(c), which is needed to explain an almost
      flat top of the electric dipole resonance.
      \label{fig:spectra}
    }%
  }
\end{figure}
To study spectral properties of structures with large ACS which we
obtained by the optimization, in Fig.~\ref{fig:spectra} we plot three
different cases for designs that correspond to local maxima of $Q_{\rm
  abs}$ shown in Fig.~\ref{fig:overview}~(a).  As expected, the design
corresponding to the maximum absorption efficiency at $R=36$~nm has a
single electric dipole resonance centered at the target wavelength
$\lambda=500$~nm. Spectra of designs with maxima at $R=63$~nm and
$R=81$~nm have a signature of the superabsorption, i.e. there is an
overlap of several resonances.  We note that these structures have
additional absorption resonances, but they are located far from the
wavelength of interest.  A noticeable feature of
Fig.~\ref{fig:spectra}~(c) is an almost flat top of the electric
dipole resonance. More detailed analysis shows that we have {\em
  excited several electric dipole resonances} with close resonance
frequencies within our multilayer structure. Indeed, if we plot a
superposition of the squares of the absolute values of the Mie
coefficients, which characterize electric energy density stored in
each layer, we find that we excite resonances in all three layers, and
they are slightly offset as shown in
Fig.~\ref{fig:spectra}~(d). Combined effect of these resonances
produces the flat and relatively broadband electric resonance response
shown in Fig.~\ref{fig:spectra}~(c).

\begin{figure}[h]
  \center{
    % Use pdfcrop to remove white margins
    \includegraphics[width=0.47\textwidth]{SiAgSi-flow-R62-YZ-Eabs}%
    \caption{Amplitude of electric field for $R=36$~nm (a,c) and
      superabsorbing designs (b,d) in E-k  (a-b) and H-k (c-d)
      planes normalized to incident wave.  White curves show the
      energy flow streamlines, plane wave comes from the left.
      \label{fig:field}
    }%
  }
\end{figure}
Finally, we present distribution of the amplitude of the electric
field in Fig.~\ref{fig:field} for two designs: with the best
efficiency at $R=36$~nm and in a superabsorbing design with $R=63$~nm.
Using semi-transparent white curves we also plot streamlines of the
Poynting vector which characterize energy flow.  For the effective
design of the absorber, the power from a large cross-sectional area
flows into the particle.  In case of superabsorption regime, we
observe the formation of vortices in the power flow, which make
absorption more efficient as the electromagnetic energy propagates
several times through the absorbing materials.  The reason for the
smaller overall absorption efficiency of a superabsorbing design is
obvious: spatial distribution of the electric field is not uniform
inside the particle and the share of the volume with high absorption
rate in the vortices does not compensate low absorption efficiency in
the regions with small electric field (absorbed power is expressed as
$P_{\rm abs}=\frac{1}{2}\int\sigma \left|E\right|^2dx\,dy\,dz$)

The stochastic algorithm utilized in our approach is very generic and
the optimization can be repeated for any desired wavelength or
wavelength range.  As a result, one can design absorbers with broad
spectra or spectrally-selective absorbers with almost arbitrary
prescribed properties.  One can also achieve broadband performance by
mixing particles whose absorption is optimized for different
wavelengths. We have verified that due to strong localization of
electric dipole field it is possible to design dimers whose absorbing
properties are dominated by the properties of individual particles,
and not by their mutual interaction. As a result, by appropriately
spacing the resonances of individual particles, their mixture will
exhibit a combined broadband response. Providing such an additional
control, this approach complements the case of self-organized
particles of various size and shape, which was experimentally proved
to have a wide absorption band~[ACS-AMI-Liu-2015]. % Reference to the
% paper mentioned with the reviewer in his second comment.
Further control of the absorption spectrum can be achieved by
arranging our spherical structures in a periodic and non-periodic
arrays.

We note, that using this algorithm, one can optimize not
only absorbtion efficiency, but also other parameters that may be
desired for some applications. As an example we reproduce some of the
results from the work of Estakhri and Al\`u,\cite{Alu-2014} where
authors aim to design absorbers with small scattering cross-section,
and we provide a number of new optimized designs. The efficiency in
the Ref.\cite{Alu-2014} is defined as the ACS normalized to
scattering cross-section. Initially, we set the total value of the
absorbed power with cross-section of $\alpha_{\rm
  abs}=\frac{3\lambda^2}{8\pi}$ and keep the outer radius of the
particle fixed. In this case the optimization gives a result similar
to the structure with contributing harmonics TM${_1}$ and TE$_1$ from
Ref.\cite{Alu-2014}  For $\epsilon_1 = 1.29+i0.01$, $\epsilon_2 =
-10.37+ i0.35$, and $\epsilon_3=8.4+i2.33$ as material parameters we
obtained radii $\{a_{c1},a_{c2},a_3\}=\{0.142,0.166,0.194\}\lambda$
and scattering-normalized absorption efficiency $\eta_{\rm
  abs}^{(\alpha)} =7.65$ which corresponds to $\eta_{\rm
  abs}^{(\alpha)} =7.1$ from the original work.\cite{Alu-2014}
However, if we set the optimizer to keep high level of absoption
efficiency $Q_{\rm abs} \approx 5$ the particle becomes much smaller
and the size of the outer layer vanishes
$\{a_{c1},a_{c2}\}=\{0.00635,0.00747\}\lambda$ resulting in $\eta_{\rm
  abs}^{(Q)} =544$.  It means that this small particle still absorbs
five times its phisical size with a very large scattering-normalized
absorption efficiency.

@@

  Thanks to David A. Powell for his contribution to the analysis of
  the spectrum feature.  AEM and IVS acknowledge the support from the
  Australian Research Council through Future Fellow and Discovery
  project schemes. OPR is grateful to Consejo Nacional de Ciencia y
  Tecnolog\'{i}a (Mexico) for financing a short stay at Universidad
  Autónoma de Puebla, Mexico.  KSL and PAB thank the Ministry of
  Education and Science of the Russian Federation and Government of
  the Russian Federation (Grant 074-U01) for the financial support.

>>>>

\sffamily{\textbf{  Nanoparticles have a fundamental limit as to how much light they can
  absorb. This limit is based on the finite number of modes excited in
  the nanoparticle at a given wavelength and maximum absorption
  capacity per mode. The enhanced absorption can be achieved when each
  mode supported by the nanoparticle absorbs light up to the maximum
  capacity. Using stochastic optimization algorithm, we design
  multilayer nanoparticles, in which we can make several resonant
  modes overlap at the same frequency resulting in \textit{
    superabsorption}.  We further introduce the \textit{ efficiency of the
    absorption} for a nanoparticle, which is the absorption normalized
  by the physical size of the particle, and show that efficient
  absorbers are not always operating in the superabsorbing regime.}}\\%The abstrast goes here instead of the text "The abstract should be..."

@@

Mie theory,\cite{Mie-1908} which is over 100 years old, describes
interaction of electromagnetic waves with spherical particles. Mie
solution is still of great interest these
days,\cite{Suzuki-2008,MacKowski-2012,Lerme-2000,Xu-2005,Li-2006,Gogoi-2010,Santiago-2011}
since it is one of the primary tools for analyzing wave scattering by
spherical objects. Further development of the Mie
theory\cite{Yang-2003, Pena-scattnlay-2009} made it possible to apply
it to the study of multilayer spherical
particles.\cite{Sheehan-2013,Selmke-2012}  Such particles have
various applications in cancer treatment,\cite{Zhang-2010,
  Hirsch-2003} medical diagnostics,\cite{Allain-2002}
cloaking\cite{Qui-2009, Semouchkina-2013, Ladutenko-2014} and
plasmonic devices,\cite{Liu-MatLett-2015, Martin-2013, Alu-2005, Liu-Nanotech-2013} in the study of
thermal properties of insulating materials,\cite{Xie-2013} as well as
for improving performance of solar cells.\cite{Kameya-2011,Mann-2011}

@@

Similar fundamental limitations exist for the absorbing properties of
subwavelength nanoparticles.  Tribelsky\cite{Tribelsky-2011} has
derived a theoretical limit of a maximum absorption cross-section
(ACS) value for a single channel, i.e., when only one mode of a sphere
is excited.  As a result, the absorption coefficients $\tilde{a}_n=
{\rm Re}\{a_n\} - |a_n|^2 $ and $\tilde{b}_n= {\rm Re}\{b_n\} -
|b_n|^2 $ become limited by $1/4$, here $a_n$ and $b_n$ are scattering
coefficient as defined within the Mie theory\cite{Bohren-1983} for the
expansion of the scattered electric field:
\[
{\rm \mathbf{E}}_s = \sum_{n=1}^{\infty} E_n \left( i a_n {\rm
    \mathbf{N}}_{e1n}^{(3)} - b_n{\rm\mathbf{M}_{o1n}^{(3)}} \right),
\]
where ${\rm \mathbf{N}}_{e1n}^{(3)}$ and ${\rm\mathbf{M}_{o1n}^{(3)}}$
are corresponding vector spherical harmonics,
$E_n=i^nE_0(2n+1)/n(n+1)$, $n$ is the angular momentum of the mode,
and $E_0$ is the amplitude of the incident field.

To overcome these limitations, we employ similar approach to the one
used for enhancing scattering cross-section.\cite{Fan-2011} In
particular, we propose to use the multilayer structures, and by means
of stochastic optimization algorithm\cite{Jingqiao-JADE-2009} we
optimize the ACS of such nanoparticles. We analyze the absorption
cross-section of these particles, and present the superabsorption
regime. We further introduce the absorption efficiency, which is the
ACS normalized to the geometric cross-section of particles. The absorption efficiency can be made large either by increasing ACS while keeping the particle size fixed, or by decreasing the particle size for fixed ACS. As a result, we show in this paper that smaller particles are more efficient when they operate in a single mode regime, while larger particles are more efficient absorbers when multiple modes are excited at the same frequency.

Another approach for an ideal absorber is given in the recent work by
Grigoriev et al.\cite{Grigoriev-2015} Authors considered only dipole
approximation, and the final result is very close to the dipole limit
predicted by Tribelsky.\cite{Tribelsky-2011}  Such absorption design
corresponds to the single mode limit.  At the same time, Grigoriev et
al.\cite{Grigoriev-2015} also provide an equation to design a
core-shell structure from given materials. However, in the case of
$Si$ core and $Ag$ shell materials and sizes taken from the best
design obtained in the present paper, their equation gives a complex
value for the core material filling factor, which cannot be achieved
in experimental realizations.

@@

The proposed approach can be applied to arbitrary combination of
materials, but to be more specific in what follows we consider
dielectric-metal-dielectric triple-layer $Si/Ag/Si$ spherical particle
illuminated by a plane wave schematically shown in
Fig.~\ref{fig:geom}. In this work we describe the materials using
experimentally measured parameters from Ref.,\cite{palik-1997}
e.g. at $\lambda = 500$ nm $\epsilon_{Si} = 18.5 + i0.63$ and
$\epsilon_{Ag} = -8.5 + i0.76$.  To optimize the thickness of each
layer we implemented\cite{JADE-web} an adaptive differential
evolution algorithm,\cite{Storn-DE-first-1997} which is called
JADE.\cite{Jingqiao-JADE-2009}  The technical details of the
optimization algorithm were published previously in
Ref.\cite{Ladutenko-2014} We perform Mie calculations using the
Scattnlay software,\cite{Pena-scattnlay-2009,Scattnlay-web} whose
results are verified by a number of other implementations of the Mie
solutions and by commercially available software including CST
Microwave studio\cite{CST-web} and Comsol Multiphysics.\cite{Comsol-web}

@@

\begin{figure}[h]
  \center{
    % Use pdfcrop to remove white margins
    \includegraphics[width=0.45\textwidth]{2015-04-01-SiAgSi-ab-spectra4}%
    \caption{Spectra of Mie absorption coefficients of (a)~efficient
      and (b-c)~superabsorption design. Panel~(d) shows the
      superposition of the squared absolute values of the Mie
      coefficients for electric dipole contribution inside each layer
      of design from panel~(c), and it explains an almost
      flat top of the electric dipole resonance.
      \label{fig:spectra}
    }%
  }
\end{figure}
To study spectral properties of structures with large ACS which we
obtained by the optimization, in Fig.~\ref{fig:spectra} we plot three
different cases for designs that correspond to local maxima of $Q_{\rm
  abs}$ shown in Fig.~\ref{fig:overview}~(a).  As expected, the design
corresponding to the maximum absorption efficiency at $R=36$~nm has a
single electric dipole resonance centered at the target wavelength
$\lambda=500$~nm. Spectra of designs with maxima at $R=63$~nm and
$R=81$~nm have a signature of the superabsorption, i.e. there is an
overlap of several resonances.  We note that these structures have
additional absorption resonances, but they are located far from the
wavelength of interest.  A noticeable feature of
Fig.~\ref{fig:spectra}~(c) is an almost flat top of the electric
dipole resonance. More detailed analysis shows that we have {\em
  excited several electric dipole resonances} with close resonance
frequencies within our multilayer structure. Indeed, if we plot a
superposition of the squares of the absolute values of the Mie
coefficients, which characterize electric energy density stored in
each layer, we find that we excite resonances in all three layers, and
they are slightly offset as shown in
Fig.~\ref{fig:spectra}~(d). Combined effect of these resonances
produces the flat and relatively broadband electric resonance response
shown in Fig.~\ref{fig:spectra}~(c).

\begin{figure}[h]
  \center{
    % Use pdfcrop to remove white margins
    \includegraphics[width=0.47\textwidth]{SiAgSi-flow-R62-YZ-Eabs}%
    \caption{Amplitude of electric field for $R=36$~nm (a,c) and
      superabsorbing designs (b,d) in E-k  (a-b) and H-k (c-d)
      planes normalized to the incident wave.  White curves show the
      energy flow streamlines; plane wave comes from the left.
      \label{fig:field}
    }%
  }
\end{figure}
Finally, we present distribution of the amplitude of the electric
field in Fig.~\ref{fig:field} for two designs: with the best
efficiency at $R=36$~nm and in a superabsorbing design with $R=63$~nm.
Using semi-transparent white curves we also plot streamlines of the
Poynting vector which characterize energy flow.  For the effective
design of the absorber, the power from a large cross-sectional area
flows into the particle.  In case of superabsorption regime, we
observe the formation of vortices in the power flow, which make
absorption more efficient as the electromagnetic energy propagates
several times through the absorbing materials.  The reason for the
smaller overall absorption efficiency of a superabsorbing design is
obvious: spatial distribution of the electric field is not uniform
inside the particle and the share of the volume with high absorption
rate in the vortices does not compensate low absorption efficiency in
the regions with small electric field (absorbed power is expressed as
$P_{\rm abs}=\frac{1}{2}\int\sigma \left|E\right|^2dx\,dy\,dz$)

The stochastic algorithm utilized in our approach is very generic and
the optimization can be repeated for any desired wavelength or
wavelength range.  As a result, one can design absorbers with broad
spectra or spectrally-selective absorbers with almost arbitrary
prescribed properties.  One can also achieve broadband performance by
mixing particles whose absorption is optimized for different
wavelengths. We have verified that due to the strong localization of
electric dipole field it is possible to design dimers whose absorbing
properties are dominated by the properties of individual particles,
and not by their mutual interaction. As a result, by appropriately
spacing the resonances of individual particles, their mixture will
exhibit a combined broadband response. Providing such an additional
control, this approach complements the case of self-organized
particles of various size and shape, which was experimentally proven
to have a wide absorption band~[ACS-AMI-Liu-2015]. % Reference to the
% paper mentioned with the reviewer in his second comment.
Further control of the absorption spectrum can be achieved by
arranging our spherical structures in a periodic and non-periodic
arrays.

We note, that using this algorithm, one can optimize not
only absorption efficiency, but also other parameters that may be
desired for some applications. As an example we reproduce some of the
results from the work of Estakhri and Al\`u,\cite{Alu-2014} where
authors aim to design absorbers with small scattering cross-section,
and we provide a number of new optimized designs. The efficiency in
the Ref.\cite{Alu-2014} is defined as the ACS normalized to
scattering cross-section. Initially, we set the total value of the
absorbed power with cross-section of $\alpha_{\rm
  abs}=\frac{3\lambda^2}{8\pi}$ and keep the outer radius of the
particle fixed. In this case the optimization gives a result similar
to the structure with contributing harmonics TM${_1}$ and TE$_1$ from
Ref.\cite{Alu-2014}  For $\epsilon_1 = 1.29+i0.01$, $\epsilon_2 =
-10.37+ i0.35$, and $\epsilon_3=8.4+i2.33$ as material parameters we
obtained radii $\{a_{c1},a_{c2},a_3\}=\{0.142,0.166,0.194\}\lambda$
and scattering-normalized absorption efficiency $\eta_{\rm
  abs}^{(\alpha)} =7.65$ which corresponds to $\eta_{\rm
  abs}^{(\alpha)} =7.1$ from the original work.\cite{Alu-2014}
However, if we set the optimizer to keep high level of absorption
efficiency $Q_{\rm abs} \approx 5$ the particle becomes much smaller
and the size of the outer layer vanishes
$\{a_{c1},a_{c2}\}=\{0.00635,0.00747\}\lambda$ resulting in $\eta_{\rm
  abs}^{(Q)} =544$.  It means that this small particle still absorbs
five times its physical size with a very large scattering-normalized
absorption efficiency.

@@

  Authors wish to thank David A. Powell for useful discussions.  AEM and IVS acknowledge the support from the Australian Research Council through Future Fellow and Discovery
  Project schemes. OPR is grateful to Consejo Nacional de Ciencia y
  Tecnolog\'{i}a (Mexico) for financing a short stay at Universidad
  Autónoma de Puebla, Mexico.  KSL and PAB thank the Ministry of
  Education and Science of the Russian Federation and Government of
  the Russian Federation (Grant 074-U01) for the financial support.
